The Migration of the Field Code

### 2016-02-17 talks/dh-working-group/dh-working-group.Rmd
No date; better citation

---
title: "The Migration of the Field Code"
author: "Kellen Funk and Lincoln Mullen"
output: tufte::tufte_handout
date: "February 17, 2016"
---

\begin{abstract}
This handout describes our work in progress for the Digital Humanities Working Group at George Mason University.\\
E-mail: \url{lincoln@lincolnmullen.com}, \url{kfunk@princeton.edu}
\end{abstract}

@@

We found out how the codes borrowed from one another by splitting the codes into sections and comparing each section to every other section.^[The data and code to re-run our analyses are available in a GitHub repository: <https://github.com/lmullen/civil-procedure-codes>. We generalized our method in Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.2 (2015): <https://github.com/ropensci/textreuse>, which was peer-reviewed by rOpenSci. We benefitted a great deal from  David A. Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86–94, doi:10.1109/BigData.2013.6691675; David A. Smith et al., "Detecting and Modeling Local Text Reuse," in *Proceedings of the 14th ACM/IEEE-CS Joint Conference on Digital Libraries* (IEEE Press, 2014), 183–92, <http://dl.acm.org/citation.cfm?id=2740800>.] This process in essence mimicked the way that nineteenth-century code commissioners literally cut and pasted sections from other jurisidictions.

>>>>

---
title: "The Migration of the Field Code"
author: "Kellen Funk and Lincoln Mullen"
output: tufte::tufte_handout
---

\begin{abstract}
This paper describes our work in progress for the Digital Humanities Working Group at George Mason University on February 17, 2016.\\
E-mail: \url{lincoln@lincolnmullen.com}, \url{kfunk@princeton.edu}
\end{abstract}

@@

We found out how the codes borrowed from one another by splitting the codes into sections and comparing each section to every other section.^[The data and code to re-run our analyses are available in a GitHub repository: <https://github.com/lmullen/civil-procedure-codes>. We generalized our method in Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.2 (2015): <https://github.com/ropensci/textreuse>, which was peer-reviewed by rOpenSci. We benefitted a great deal from  David A. Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86–94, doi:10.1109/BigData.2013.6691675, and the other publications of the Viral Texts team.] This process in essence mimicked the way that nineteenth-century code commissioners literally cut and pasted sections from other jurisidictions.
